Matching bullets

### 2015-11-23 imaging-paper.Rnw
Discussion of residual plot creation in application

>>>>

The application includes a button which allows the automatic creation of a residual plot. An x coordinate value can be selected, and a cross-section of the two bullet at the x value will be taken. The previously described Loess regression procedure will be applied to the two cross sections. A residual plot will be produced beneath the surface plots allowing for an assessment of the similarity of the markings. It is intended that users will perform this procedure at different x values in order to see whether the markings indicate a match at different points along the bullet.
